Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-14 nlp.tex
added rules that define initial probability weight assignment

<Day>     ::= d d (between 01 and 28-31, depending on month/year);

@@

<TwelveHour> ::= d d (between 00-12);

<TwentyFourHour> ::= d d (between 00 and 23);

@@

@@

(add the rules for how probabilistic weights are assigned to the CFG)
(show cfg with prob values)
(examples -> one ambiguous, one not)
(parse tree with final probability weights)

>>>>

<Day>     ::= dd (between 01 and 28-31, depending on month/year);

@@

<TwelveHour> ::= dd (between 00-12);

<TwentyFourHour> ::= dd (between 00 and 23);

@@

(add notation for how rules are defined)

@@

In order to bootstrap the probability weights in the \texttt{PCFG}, we manually set initial probability weights to various rules in the grammar as follows:
\begin{itemize}
\item Similar to the MDL ranking properties described in Section 3.7, rules involving the non-terminal \texttt{DateGrammar} on the left-side of the rule, are assigned probability weights higher than those rules with the non-terminal being \texttt{TimeGrammar}. In practice, assigning $p(\texttt{DateGrammar} \rightarrow \beta_{1}) = 0.9$ and $p(\texttt{TimeGrammar} \rightarrow \beta_{2}) = 0.7$ leads to optimal ranking of the parse trees.

\item For the non-terminal symbol \texttt{Day}, the constraint specified is a range between 01 and 28-31, depending on month/year. However, for \texttt{dd} $> 12$, $p(\texttt{Day} \rightarrow d d) = 1.0$, and $0.5$ otherwise. This assignment helps disambiguate days from months.

(show cfg with prob values)
(examples -> one ambiguous, one not)
(parse tree with final probability weights)
